---
title: "Guided Project: NY Solar Resource Data"
author: "Michael Hoang"
date: "22/03/2021"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
setwd("~/MyDatasets")
options(scipen = 999)

```


# INTRODUCTION

The goal of this project is to get some first hand experience extracting data from the [US Public Data](https://api.data.gov/docs/).  Specifically, we'll be getting data pertaining to solar data for the state of New York.   

# Finding suitable endpoint and parameter to query the API

```{r}

api_key = "637PPdo7heBuvPuAiDOraIj8zvbdZdCdMdp2OxjA"

api_url <- "https://developer.nrel.gov/api/solar/solar_resource/v1.json"

lat = 41

lon = -75

parameter_list = list(api_key = "637PPdo7heBuvPuAiDOraIj8zvbdZdCdMdp2OxjA", lat = 41, lon = -75)

```

# Extracting the NY Solar Resource Data 

```{r}

library(httr)

response <- GET(api_url, query = parameter_list) # API request 
status = status_code(response) # to track error 
response_type = http_type(response) # Display the API response format
content = content(response, "text") # extracting the API content 

response
status
response_type
content

```

# Parsing the JSON into R Object 

```{r}

json_list = jsonlite::fromJSON(content)
str(json_list)

```

# Creating a dataframe from a complex list 

```{r}

outputs_list = json_list$outputs

avg_dni = outputs_list$avg_dni$monthly
avg_ghi = outputs_list$avg_ghi$monthly
avg_lat_tilt = outputs_list$avg_lat_tilt$monthly

df = tibble::tibble(
  "month" = month.abb, 
  "avg_dni" = avg_dni, 
  "avg_ghi" = avg_ghi, 
  "avg_lat_tilt" = avg_lat_tilt
)

simplified_output_list <- unlist(outputs_list)
data_matrix = matrix(data = simplified_output_list, nrow = 13)
data_matrix = data_matrix[-1,]
another_df = as.data.frame(data_matrix)
another_df


```

# Putting it all together 

```{r}
library(tidyverse)
library(dplyr)
```

```{r}
nrel_api_json_get_df <- function(endpoint, queries = list()) {
  ## Preparing the URL 
  url <- modify_url("https://developer.nrel.gov", path = endpoint)
  ## Querying the API
  response <- GET(url, query = queries)
  ## Tracking errors
  if ( http_error(response) ){
    print(status_code(response))
    print(http_status(response))
    stop("Something went wrong.", call. = FALSE)
  }
  if (http_type(response) != "application/json") {
    stop("API did not return json", call. = FALSE)
  }
  ## Extracting content
  json_text <- content(response, "text")
  ## Converting content into Dataframe
  table_lst <- jsonlite::fromJSON(json_text)
  dataframe <- tibble::tibble("month" = month.abb,
                              "avg_dni" = as.numeric(table_lst$outputs$avg_dni$monthly),
                              "avg_ghi" = as.numeric(table_lst$outputs$avg_ghi$monthly),
                              "avg_lat_tilt" = as.numeric(table_lst$outputs$avg_lat_tilt$monthly))
  ## Returning the dataframe  
  dataframe
}
# Using the custom `nrel_api_json_get_df()` function to extract the solar resource as a dataframe
## Providing the `"api/solar/solar_resource/v1.json"` as the `endpoint` parameter
## Providing the `parameters_list` variable as `queries` parameter
solar_resource_df <- nrel_api_json_get_df("api/solar/solar_resource/v1.json", parameter_list)
# Printing the output dataframe
solar_resource_df

```

# Visualize NYC Solar Resource 

```{r}

ggplot(data = solar_resource_df,
       aes(x = month, y = avg_dni, group = 1)) +
  geom_line() +
  geom_point() +
  theme_bw()
# Converting the `month` column into factor using the following command  
solar_resource_df <- solar_resource_df %>% 
  mutate(month = factor(month, levels = month.abb))
# Replotting the `avg_dni` value for each month 
ggplot(data = solar_resource_df,
       aes(x = month, y = avg_dni, group = 1)) +
  geom_line() +
  geom_point() +
  theme_bw()


```

