---
title: 'Guided Project: Mobile App for Lottery Addiction'
author: "Michael Hoang"
date: "24/07/2020"
output: html_document
---

In this guided project, we will be working as an employee aiding in the design of a mobile app intended to help lottery addicts to realistically understand their chances of winning. Considering that the fun of winning can escalate into a habit and then to an addiction that can spiral towards accumulating debt that results in situations 
that are not favorable, it would make sense to develop such an app. Specifically, you will be working as a data analysttasked with building the logic behind this app and to calculate probabilities of winning. 

For the first version of this app, we will be focusing on the Ontario lottery [6/49](https://en.wikipedia.org/wiki/Lotto_6/49). This lottery essentially involves choosing a set of 6 numbers from 1 to 49 with a graded prizes depending on the degree of matching. For our analysis, we will be looking at a [dataset](https://www.kaggle.com/datascienceai/lottery-dataset) of 3665 drawings from 1982 to 2018. Ultimately we would like to answer the following questions:
  
  - What is the probability of winning the big prize with a single ticket?
  - What is the probability of winning the big prize if we play 40 different tickets (or any other numbers)?
  - What is the probability of having at least five(or four or three or two) winning number on a single ticket?


```{r setup, include=FALSE}
# ENTERING LIBRARIES THAT I NEED FOR CONDUCTING THIS PROJECT

library(tidyr)
library(purrr)
library(stringr)
library(dplyr)
library(ggplot2)
library(tibble)
library(readr)
library(aod)
library(epiR)
library(Rcpp)
library(nnet)
library(car) 
library(survival) #
library(survminer)
library(lmtest)
library(rms) 
library(ggfortify) 
library(sets)

# Loading the CSV file 

lotto = read.csv("C:/Users/micha/Downloads/649.csv")
View(lotto)

```

STEP 2: Writing Core Functions 

Since we will need to calculate factorials, combinations and such throughout this analysis, we will need to create functions for these calculations. Remember that permutations is used to calculate the probabilities of an event where where the sampling involves no replacement and order matters. However in the instance where it does not matter, then we will be using combination. 

```{r}

factorial <- function(n) {
  final_number <- 1
  final_number <- as.numeric(final_number)
  for (i in 1:n){
    final_number <- final_number * i
  }
  return(final_number)
}

permutation <- function(n, k) {
  final <- factorial(n) / factorial(n-k)
  final <- as.numeric(final)
  return(final)
}

combination <- function(n, k){
  part_a <- factorial(n)/factorial(n-k)
  part_b <- 1/factorial(k)
  final <- part_a * part_b
  final <- as.numeric(final)
  return(final)
}

```

STEP 3: One-Ticket Probability

In the 6/49 lottery, you will select six numbers from a set of 49 numbers ranging from 1 to 49. The player wins the big prize (essentially a large portion of the pooled pot worth millions) if all of the 6 numbers match the chosen draw numbers. This does not include the bonus number that can also be selected for an additional cost. For the rest of the outcomes, it will be a prize ranging from a free play to a small share of the jackpot pool. 

Knowing this, we want to be able to calculate the probability of winning the big prize (i.e. 6/6) with the various numbers available on a single ticket. There are a few things that was made aware to us when formulating a means to determine this:

  - user inputs six diferent numbers from 1 to 49
  - the six numbers will come as a R vector which will serve as a single input
  - print out the probability in a friendly way (i.e. make it so that really simple that a 10 year old can understand)


PART A: Total possible combinations for a single ticket

total_combo = combination(49, 6) # 13983816 total possible combinations to get all 6 numbers right


PART B: Input and percentages 

Understanding that this entailed function will have the participant input a single combination of 6 values, which will be in the form of a vector (i.e. c(#,#,#,#,#,#)) the likelihood of an outcome would be 1 / 13983816. 

options(scipen = 999) # Used to get rid of scientific notation 
probability = round((1/total_combo) * 100, 9)
    

PART C: Creating a message  

From the probability, we want to then turn it into a string and then paste it on a statement that 
says "You have a ______ % chance of getting the big prize."

probability <- as.character(probability)
statement <- cat("You have a " , , "% chance of winning the big prize.", sep = "")


PART D: Putting it all together into a single function

```{r}

one_ticket_probability = function(numbers) {
  total_combo = combination(49, 6)
  probability = round((1/total_combo) * 100, 9) 
  probability = as.character(probability)
  statement = cat('You have a ', probability, '% chance of winning the big prize.', sep = '')
  return(statement)
} 

test <- one_ticket_probability(c(1,2,3,4,5,6))

```

STEP 4: Historical Data Check 

For the first version of the app, users should be able to compare their ticket against past winning combinations in the historyical lottery data in Canada. For now, lets check out the dataset. 

```{r}

num_cols <- length(lotto)
num_rows <- count(lotto) 

dimensions <- dim(lotto)

head(lotto, 3)
tail(lotto, 3)


```

STEP 5: New Data structure

```{r}

data1 = c(1,3,5)
data2 = c(2,4,6)
data3 = c(8,9,7)

unnamed_list <- list(data1, data2, data3)
first_vector <- unnamed_list[[1]]

named_list <- list(first = data1, second = data2, third = data3)
first_item_sum <- named_list$first[1] + named_list$second[1] + named_list$third[1]

```

STEP 6: Using PMAP

```{r}

data_list = list(data1, data2, data3)

sums = pmap(data_list, function(x,y,z) {x+y+z})

averages <- pmap(data_list, function(x,y,z) {(x+y+z)/3})
first_average <- unlist(averages)[1]

```

STEP 7: Function for Historical Data Check

Now that we have an idea of the makeup of the data set, we want to now create a function that will enableusers to compare their ticket against historical lottery data in Canada and determine whether they would have ever won by now.

Some details that we need to be aware of:
  - inside the app, user will input six different numbers from 1 to 49
  - under the hood, the six numbers will come as an R vector and serve as an input to our function
  - the engineering team want us to write a function that prints:
    > the number of times the combination selected occured in the Canada data set
    > the probability of winning the big prize in the next drawing with that combination


Part A: Extracting the six winning numbers in a column

We want to create a way to be able to extract the 6 numbers from the columns [NUMBER.DRAWN.1 - NUMBER.DRAWN.6]. Ideally, we want to use the pmap function which requires a list entry, then a function of some sort. So the first step should be to create a list with these 6 numbers. 

```{r}

list_test <- list(
  a <- lotto$NUMBER.DRAWN.1,
  b <- lotto$NUMBER.DRAWN.2,
  c <- lotto$NUMBER.DRAWN.3,
  d <- lotto$NUMBER.DRAWN.4,
  e <- lotto$NUMBER.DRAWN.5,
  f <- lotto$NUMBER.DRAWN.6
) 

class(list_test)

```

Now that we have a list of values, we will now want to convert this into a vector which should have 3665 rows of them.

```{r}

winning_numbers <- pmap(list_test, function(a,b,c,d,e,f) {c(a,b,c,d,e,f)})
View(winning_numbers)
head(winning_numbers)
lotto$winning_numbers <- winning_numbers

```

PART B: Create the function

Now that I created a list, I want to finally make the function that takes in two inputs: 
(1) an R vector containing the user numbers 
(2) the list containing the sets of winning numbers (i.e. that thing that I just made in PART A)

So the input of the new function should be something along the lines of:

some_name <- function(my_numbers, winning_numbers) {
    SOMETHING THAT COMPARES MY NUMBERS TO PAST NUMBERS,
    SOMETHING THAT PRINTS OUT NUMBER OF TIMES THAT MY NUMBERS MATCHES PAST NUMBERS,
    SOME PHRASE INDICATING THAT MY SET OF NUMBERS HAS X% OF WINNING THE BIG PRIZE
  
  return the phrase  
  }

To compare my numbers to past numbers, I will need to use the setequal function which will match TRUE or FALSE depending if all of the entries of a given list will match the reference list (irregardless of order)

Ex. 

```{r}

set_a <- c('Foo', "Bar", "Baz")
set_b <- c("Not", 'At', 'All')
set_c <- c("Foo", "Baz", "Bar")
set_d <- c("Foo", "Bar", "Baz", "Not, At")
set_e <- c("Bar", "Baz", "Foo", "Foo", "Baz")

# setequal(test_list, reference_list)

setequal(set_a, set_b) # FALSE
setequal(set_a, set_c) # TRUE
setequal(set_a, set_d) # FALSE
setequal(set_a, set_e) # TRUE

```

Thought process: I will need to use the map function since I am going down a series of rows to find matches. Additionally, this should be saved into a variable like "match"

map(list, function(x) {setequal(list, ref_list)})

```{r}

match <- map(my_numbers, function(x) {setequal(x, winning_numbers)})
    
    
test_a <- function(nums, past_winners = winning_numbers) {
      historical_match <- map(past_winners, function(x) {setequal(x, nums)})
      return(historical_match)
    }
    
sample_a <- test_a(c(3,11,12,14,41,43))
    
class(sample_a)

# With this test, I ended up getting a giant print out of TRUE + FALSES. So, at the very least, there is an outcome
    
    
test_b <- function(nums, past_winners = winning_numbers) {
      historical_match <- map(past_winners, function(x) {setequal(x, nums)})
      historical_match <- unlist(historical_match)
      return(historical_match)
    }
    
sample_b <- test_b(c(3,11,12,14,41,43))
    
class(sample_b)
    
# With this test, I unlisted the return, so that now it return a different type of variable. In this case, it's a logical
    
```

Knowing that I now have a variable that stores the results of whether my set of numbers match the reference list, I want to know the number of times that these matches. Likely, I will need to get the sum of the counts of some kind. 

```{r}

test_c <- function(nums, past_winners = winning_numbers) {
      historical_match <- map(past_winners, function(x) {setequal(x, nums)})
      counts <- sum(unlist(historical_match))
      return(counts)
    }
    
sample_c <- test_c(c(3,11,12,14,41,43)) 
    
# With this test, it return the count of the number of matches that exists within the reference list  that matches my entries
  
```

Lastly, I want to create a phrase that will let the person know if this set of numbers was a winning set in the past.  

```{r}

test_d <- function(nums, past_winners = winning_numbers) {
        historical_match <- map(past_winners, function(x) {setequal(x, nums)})
        counts <- sum(unlist(historical_match))
        phrase <- cat("This set of numbers that you've entered matched ", counts, " times in the past lotto 6/49 draws.", sep = "")
        return(phrase)
      }
      
sample_d <- test_d(c(3,11,12,14,41,43)) 
      
# So this test seems to work. However, it's phrasing can be improved upon by differentiating b/t never been pulled, only once and more than once.  

historical_check <- function(nums, past_winners = winning_numbers) {
        historical_match <- map(past_winners, function(x) {setequal(x, nums)})
        counts <- sum(unlist(historical_match))
        phrase <- ifelse(counts == 1, "This set of numbers that you've entered has been pulled once in past lotto 6/49 draws. The odds that you will win the big prize is 0.0000072%.", ifelse(counts == 0, "This set of numbers that you've entered has never been pulled once in previous lotto 6/49 draws. The odds that you will win the big prize is 0.0000072%.", cat("This set of numbers that you've entered matched ", counts, " times in the past lotto 6/49 draws. The odds that you will win the big prize is 0.0000072%.", sep = "")))
        return(phrase)
      }
      
sample_e <- historical_check(c(3,11,12,14,41,43))
sample_f <- historical_check(c(1,2,3,4,5,6))      

```

Ultimately, we created a function that will check whether the selected 6 numbers (entered as a vector) had previously matched winning numbers in its entirety or not and, if so, the number
of times that it did match. Considering that there was never an instance of multiple occurance of the same numbers being selected, we couldn't fully examine this function's capabilities. 




STEP 8: Multi Ticket Probability 

One situation our functions do not cover is the issue of multiple tickets. Lottery addicts usually play more than one ticket on a single drawing, thinking that this might increase their chances of winning significantly. Our purpose is to help them better estimate their chances of winning — on this screen, we are going to write a function that will allow the users to calculate the chances of winning for any number of different tickets. 

Talking with the engineering team, they gave us the following information:
  
  - The user will input the number of different tickets they want to play (without inputting the specific combinations they intend to play).
  - Our function will see an integer between 1 and 13,983,816 (the maximum number of different tickets).
  - The function should print information about the probability of winning the big prize depending on the number of different tickets played.

Ultimately our function will workout to something like this: 

multi_ticket_probability = function(num_of_tickets){
            total_possibilities <- combination(49, 6) # should come out to 13983816 possible outcomes
            chance_of_winning <- (num_of_tickets/total_possibilities) * 100 # should come down to some impossibly small number 
            phrase <- cat("Based on the number of tickets that you plan to purchase, your chance of having a winnig ticket is " , chance_of_winning, "%.", sep = "")
            return(phrase)
          }

```{r}

multi_ticket_probability = function(n) {
  total_possibilities <- combination(49,6)
  chance_of_having_one <- (n/total_possibilities) * 100
  phrase <- paste('Based on the number of tickets that you plan on purchasing, your chance of having a winning ticket is ', chance_of_having_one, "%. Fun fact, at $3 per ticket, the pot needs to be at least $52.77 million dollars if you are going to purchase every possible ticket combination just to break even and that is not considering someone else having the same set of 6 numbers.", sep = "")
  return(phrase)
} 

multi_ticket_probability(1)
multi_ticket_probability(10)
multi_ticket_probability(100)
multi_ticket_probability(1000)
multi_ticket_probability(10000)
multi_ticket_probability(100000)
multi_ticket_probability(13983816)

```

Based on this function, we can show that out of the 13983816 possible tickets choices, the odds for having a ticket with all 6 numbers is going to be impossibly small. So we will create a text that outlines this as a percentage. 

Fun fact: at $3 per ticket, the pot needs to be at least $52.77 million dollars for purchasing every possible ticket combination to just break even when considering that the big prize winner only gets 79.5% of the total pot (and that assumes you are the only one with the winning 6 numbers, otherwise it is a split pot.)




STEP 9: Less Winning Numbers 

We're going to write one more function to allow the users to calculate probabilities for two, three, four, or five winning numbers.For extra context, in most 6/49 lotteries there are smaller prizes if a player's ticket matches two, three, four, or five of the six numbers drawn. As a consequence, the users might be interested in knowing the probability of having two, three, four, or five winning numbers.

Some details to be mindful of:
  - Within the app, the user inputs (a) six different numbers from 1-49 and (b) an integer b/t 2 to 5 that represents the winning numbers expected
  - Our function prints information about the probability of having the inputted number of winning numbers

The specific combination on the ticket is irrelevant and we only need the integer between 3 and 5 representing the number of winning numbers expected. Consequently, we will write a function which takes in an integer and prints information about the chances of winning depending on the value of that integer.

The breakdown of the function 

probability_less_6 <- function(integer) {
  - Number of successful outcomes 
  - number of total possible outcomes
  - probability of number of successful outcomes and total possble outcomes
  - some text display
}


PART A: Number of successful outcomes 

combination_total = combination(6, n) # where n is the input integer

PART B: Number of total possible outcomes 

combination_remaining = combination(49-n, 6-n) 
successful = combination_total * combination_remaining

PART C: calculating probability of having matching numbers on a ticket

total_combination = combincation(49, 6)
probability = successful / total_combination * 100


PART D: Finalizing the function 

```{r}

probability_less_6 <- function(integer){
  n_successful_matches_on_ticket = combination(6, integer)  # this is to find the number of successful matches possible out of six numbers that are drawn
  n_remaining_combinations_on_ticket = combination(49 - integer, 6 - integer) # this is to find the number of matches that are left over after our projected number of correct matches out of 6 numbers drawn  
  successful_matches = n_successful_matches_on_ticket * n_remaining_combinations_on_ticket # this is the number of possible matches that I can have assuming I achieved the requested number of correctly selected numbers out of 6
  total_combination = combination(49,6) # this is the total possible combinations of all 6 numbers 
  possibility_percentage =  round((successful_matches / total_combination) * 100, 4) # percentage of the probability for me to win a prize based on the combination of correctly selected number drawn that are less than 6
  possibility = round(total_combination/successful_matches, 1) # just an inverse of the possibility percentage. 
  phrase = paste("Your chances of getting ", integer, " out of the 6 numbers drawn are ", possibility_percentage, "%. In other words, you have a 1 in ", possibility, " chance to win a prize.", sep = "")
  return(phrase)
}

probability_less_6(1)
probability_less_6(2)
probability_less_6(3)
probability_less_6(4)
probability_less_6(5)


```

UPDATE: 
  
Let us try to improve of the probability_less_6 function so that it will include a interesting statistic based on the integer entered.

```{r}

update_less_than_6 <- function(integer){
  n_successful_matches_on_ticket = combination(6, integer)  
  n_remaining_combinations_on_ticket = combination(43, 6 - integer) # refer to explanation shown [here](https://community.dataquest.io/t/guided-project-mobile-app-for-lottery-addiction-definition-of-probability-less-6/287512/2)
  successful_matches = n_successful_matches_on_ticket * n_remaining_combinations_on_ticket 
  total_combination = combination(49,6) 
  possibility_percentage =  round((successful_matches / total_combination) * 100, 4) 
  possibility = round(total_combination/successful_matches, 1) 
  phrase_1 = "Your chances of getting 1 out of 6 winning numbers drawn are 41.3019%. In other words, you have a 1 in 2.4 chance to win a prize. This is the equivalent to the world's population of people under the age of 24 (as of 2019)."
  phrase_2 = "Your chances of getting 2 out of 6 winning numbers drawn are 13.2378%. In other words, you have a 1 in 7.6 chance to win a prize. This is also the equivalent world's population of people who have genital herpes."
  phrase_3 = "Your chances of getting 3 out of 6 winning numbers drawn are 1.765%. In other words, you have a 1 in 56.7 chance of win a prize. This is the equivalent of having birth a child with Down's syndrome."
  phrase_4 = "Your chances of getting 4 out of 6 winning numbers drawn are 0.0969%. In other words, you have a 1 in 1032.4 chance to win a prize. This is lower than the chance of having given birth to triplets."
  phrase_5 = "Your chances of getting 5 out of 5 winning numbers drawn are 0.0018%. In other words, you have a 1 in 54200.8 chance to win a prize. This is the mortality rate of children with COVID-19."
  phrase_6 = "Hey dummy, you've entered a value that doesn't work here (either a zero, something greater than 5, or a decimal number). Quit being a wise ass and enter a valid number."
  phrase = ifelse(integer == 1, phrase_1,
           ifelse(integer == 2, phrase_2, 
           ifelse(integer == 3, phrase_3, 
           ifelse(integer == 4, phrase_4, 
           ifelse(integer ==  5, phrase_5, phrase_6)))))
  return(phrase)
}

winning_nums <- c(0, 1, 2, 3, 4, 5)
for (n in winning_nums) {
  print(update_less_than_6(n))
}

```

CONCLUSION

In this project we created the first version of this app which has 4 functions:

  - one_ticket_probability() — calculates the probability of winning the big prize with a single ticket
  - historical_check() — checks whether a certain combination has occurred in the Canada lottery data set
  - multi_ticket_probability() — calculates the probability for any number of of tickets between 1 and 13,983,816
  - probability_less_6() — calculates the probability of having two, three, four or five winning numbers exactly

